---
title: "Orbit-EEG TF Memory Quality Data"
output:
  html_document:
    code_folding: hide
    theme: cerulean
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

This markdown uses EEG data analyzed using the Limo Toolbox (for eeglab) to plot time-frequency beta values for overall memory quality.

```{r, include = FALSE}

### load in all necessary packages
x <- c("ggplot2", "shiny", "ggpubr", "dplyr", "knitr", "tidyr", "tidyverse", "magrittr", "grid", "gridExtra", "pander", "ez", "car", "smoothmath", "ggsignif", "formattable", "psych", "reshape2", "afex", "akima", "lsr", "readr", "scales", "mgcv", "png", "rstatix")
require(x)
lapply(x, require, character.only = TRUE)

### define computer paths
myComp <- '/Users/natalia/Desktop/orbit-EEG/'
figureDir <- paste(myComp, 'figures', sep = "") 

### define all functions
ci <- function(x) (sqrt(var(x)/length(x)))*1.96  #function to calculate 95% confidence interval
se <- function(x) sqrt(var(x)/length(x))  #function to calculate SE
jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000")) #for topoplots

### load in all memory quality TF data
myFile <- paste(myComp,'data/AllData_EEG-MQ_TF.csv', sep = "")
allData <- read.csv(myFile)

### add frequency bins (theta: 5-7 hz, alpha: 8-12 hz, beta: 13-30 hz)
allData$freqbin[c(allData$freq > 4 & allData$freq < 8)] <- 'theta'
allData$freqbin[c(allData$freq >= 8 & allData$freq <= 12)] <- 'alpha'
allData$freqbin[c(allData$freq > 12 & allData$freq <= 30)] <- 'beta'

### factor columns
allData <- allData %>% 
  mutate_if(is.character,as.factor)

```

# Memory Quality Effect - Significant TF Clusters

```{r, message=FALSE, warning=FALSE}

# subset all data to include only time points 0-4000ms (i.e., covert recall period)
allData.time <- subset(allData, time >= 0)

# Positive clusters for memory quality
cluster <- subset(allData.time, correctedP.pos < 1)
cluster$cluster <- 0

count <- 1
for (i in 1:nrow(cluster)) {
  if (i == nrow(cluster)) {break}
  else if (abs(cluster[i,1] - cluster[i+1,1]) <= 40) {cluster[i,11] <- count}
  else if (abs(cluster[i,1] - cluster[i+1,1]) > 40) {cluster[i,11] <- count; count <- count + 1}
}
cluster$cluster[cluster$cluster == 0] <- count

print(paste0("Number of positive clusters: ", count))

cluster.info <- data.frame(cluster = array(0,count), times = array(0,count), freqs = array(0,count), chans = array(0,count))
allcluster.info <- data.frame()
for (i in 1:count) {
  this.cluster <- subset(cluster, cluster == i)
  cluster.info$cluster[i] <- i
  cluster.info$times[i] <- list(round(range(this.cluster$time),2))
  cluster.info$freqs[i] <- list(round(range(this.cluster$freq),2))
  cluster.info$chans[i] <- list(unique(as.character(this.cluster$channel)))
}

# print positive clusters (NB: we're focused on negative clusters in these analyses)
positive.clusters <- cluster.info
kable(positive.clusters, caption = "Positive Cluster Information")


# Negative clusters for memory quality
cluster <- subset(allData.time, correctedP.neg < 1)
cluster$cluster <- 0

count <- 1
for (i in 1:nrow(cluster)) {
  if (i == nrow(cluster)) {break}
  else if (abs(cluster[i,1] - cluster[i+1,1]) <= 40) {cluster[i,11] <- count}
  else if (abs(cluster[i,1] - cluster[i+1,1]) > 40) {cluster[i,11] <- count; count <- count + 1}
}
cluster$cluster[cluster$cluster == 0] <- count

print(paste0("Number of negative clusters: ", count))

cluster.info <- data.frame(cluster = array(0,count), times = array(0,count), freqs = array(0,count), chans = array(0,count))
allcluster.info <- data.frame()
for (i in 1:count) {
  this.cluster <- subset(cluster, cluster == i)
  cluster.info$cluster[i] <- i
  cluster.info$times[i] <- list(round(range(this.cluster$time),2))
  cluster.info$freqs[i] <- list(round(range(this.cluster$freq),2))
  cluster.info$chans[i] <- list(unique(as.character(this.cluster$channel)))
}

# print negative clusters
negative.clusters <- cluster.info
kable(negative.clusters,  caption = "Negative Cluster Information")

```



# Memory Quality EFfect Time-Frequency Plot (all channels)

```{r, warning= FALSE, message=FALSE}

## summarize t-values by time and frequency, across all channels
MQ_TF.summary <- allData %>%
    group_by(time,freq) %>%
      summarize(t.chan = mean(tvalue)) #avg across channels

# Plot time-frequency
MQ_freqbands <- ggplot(MQ_TF.summary, aes(x=time, y=freq)) + 
  geom_tile(aes(color = t.chan, fill=t.chan), size = 2) +
  geom_vline(xintercept = 0, linetype = 2, size=0.5, color="black") +
  scale_fill_gradientn(colours = jet.colors(9), oob=squish, limits = c(-2,2)) + 
  scale_color_gradientn(colours = jet.colors(9), oob=squish,limits = c(-2,2)) +
  labs(fill = expression(paste(italic("t"), "-value")), color = expression(paste(italic("t"), "-value"))) + 
  theme(plot.tag = element_text(size = 24),
        axis.line = element_line(colour = "black"), axis.text = element_text(size=12), 
        plot.margin = unit(c(0.25,0,0.25,1), "cm"),
        panel.background = element_rect(fill = "white"),
        axis.title.x = element_text(size=22,margin = margin(t = 3)),
        axis.title.y = element_text(size=22, margin = margin(r = 8)), text = element_text(family="Avenir"), 
        legend.text = element_text(size=12,face="bold"), legend.key.width=unit(1, "cm"), legend.key.height = unit(1,"cm"))

# Change y-axis to logorithmic scale for clarity and add boxes for significant negative clusters
MQ_freqbandslog <- MQ_freqbands + scale_y_log10(name="Frequency (Hz)",breaks=c(5,10,15,20,25,30),labels=c(5,10,15,20,25,30), limits = c(5,30), expand = c(0, 0)) +
    scale_x_continuous(name="Time (ms)",  breaks=seq(-500,4000,500), expand=c(0,.01,0,.01), limits = c(-500,4000)) + 
    geom_rect(aes(xmin = 799, xmax = 918, ymin = 15.74, ymax = 29), fill = NA, color = "black", size = 1.2)+
    geom_rect(aes(xmin = 1125, xmax = 2277, ymin = 9.53, ymax = 29),fill = NA,  color = "black", size = 1.2)+
    geom_rect(aes(xmin = 2840, xmax = 3105, ymin = 5.27, ymax = 16.91), fill = NA, color = "black", size = 1.2)

print(MQ_freqbandslog)


```


# Memory Quality Effect in alpha and beta bands separately

```{r, warning=FALSE, message=FALSE}

# Summarize within each frequency band
MQ_TF_freq.summary <- allData %>%
  group_by(time,freqbin) %>%
  summarize(meanBeta = mean(mean.beta),
            meanfreq = mean(freq),
            seBeta = mean(se.beta)) #avg beta values across channels & freqbins

# Subset alpha frequency band 
MQ_TF_alpha.summary <- subset(MQ_TF_freq.summary, freqbin == "alpha")

# Plot alpha frequency across time
alpha.MQ <- ggplot(MQ_TF_alpha.summary, aes(x = time, y = meanBeta, ymin = (meanBeta - seBeta), ymax = (meanBeta + seBeta))) + 
  geom_ribbon(alpha = 0.3, fill = "#C77CFF") +
  geom_line(color = "#C77CFF", size = 0.8) + 
  geom_vline(xintercept=0, linetype="dashed", size=0.5) + geom_hline(yintercept = 0, linetype = 'dashed', size = 0.5) +
  ylab(expression(alpha)) + 
  scale_x_continuous(name="",  breaks=seq(-500,4000,500), expand=c(0,.01,0,.01), limits = c(-500,4000)) + 
  theme(plot.tag = element_text(size = 24),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(size=12), 
        plot.margin = unit(c(0.25,2.5,0.25,0.91), "cm"),
        axis.title.x = element_text(size=22,margin = margin(t = 3)),
        axis.title.y = element_text(size=22, margin = margin(r = 8)),
        legend.position = 'blank',
        panel.background = element_rect(fill = "white"),
        legend.key.width=unit(1.5, "cm"), 
        legend.key.height = unit(1.5,"cm"), 
        text = element_text(family="Avenir"))

print(alpha.MQ)

# Subset beta frequency band 
MQ_TF_beta.summary <- subset(MQ_TF_freq.summary, freqbin == "beta")

# Plot beta frequency across time
beta.MQ <- ggplot(MQ_TF_beta.summary, aes(x = time, y = meanBeta, ymin = (meanBeta - seBeta), ymax = (meanBeta + seBeta))) + 
  geom_ribbon(alpha = 0.3, fill = "#C77CFF") +
  geom_line(color = "#C77CFF", size = 0.8) + 
  geom_vline(xintercept=0, linetype="dashed", size=0.5) + geom_hline(yintercept = 0, linetype = 'dashed', size = 0.5) +
  ylab(expression(beta)) + 
  scale_x_continuous(name="Time (ms)",  breaks=seq(-500,4000,500), expand=c(0,.01,0,.01), limits = c(-500,4000)) + 
  theme(plot.tag = element_text(size = 24),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(size=12), 
        plot.margin = unit(c(0.25,2.5,0.25,0.65), "cm"),
        axis.title.x = element_text(size=22,margin = margin(t = 3)),
        axis.title.y = element_text(size=19, margin = margin(r = 8)),
        legend.position = 'blank',
        panel.background = element_rect(fill = "white"),
        legend.key.width=unit(1.5, "cm"), 
        legend.key.height = unit(1.5,"cm"), 
        text = element_text(family="Avenir"))

print(beta.MQ)


```

## Topoplot functions
#### functions from Matt Craddock (https://www.mattcraddock.com/blog/2017/02/25/erp-visualization-creating-topographical-scalp-maps-part-1/)

```{r warning = FALSE, message = FALSE}

### define custom functions for topoplot: 
theme_topo <- function(base_size = 12)
  {
  theme_bw(base_size = base_size) %+replace%
      theme(
            rect = element_blank(),
            line = element_blank(),
            axis.text = element_blank(),
            axis.title = element_blank(),
            plot.title = element_text(size=20, 
                                      margin=margin(0,0,3,0), face="plain"),  
            legend.title = element_text(size=15), legend.text = element_text(size=12),
            legend.key.width = unit(0.75,"cm"), legend.key.height = unit(0.75,"cm"),
            plot.tag = element_text(vjust = -3.5, hjust = -2),
            plot.margin = margin(0.5, 0, 0, 0, "cm")
           )
}
circleFun <- function(center = c(0,0),diameter = 1.4, npoints = 100) {
  r = diameter / 2
  tt <- seq(0,2*pi,length.out = npoints)
  xx <- center[1] + r * cos(tt)
  yy <- center[2] + r * sin(tt)
  return(data.frame(x = xx, y = yy))
}
maskRing <- circleFun() #create a circle round the outside of the plotting area to mask the jagged edges

# As it's 64 channel locations generated from EEGLab, I assume Matt Craddock's matches our locations
electrodeLocs <- read_delim("https://raw.githubusercontent.com/craddm/ExploringERPs/master/biosemi70elecs.loc",
                            "\t",
                            escape_double = FALSE,
                            col_names = c("chanNo","theta","radius","channel"),
                            trim_ws = TRUE)

# convert from polar to cartesian format:
electrodeLocs$radianTheta <- pi/180*electrodeLocs$theta
electrodeLocs <- electrodeLocs %>%
  mutate(x = .$radius*sin(.$radianTheta),
         y = .$radius*cos(.$radianTheta))

# head shape for topoplot
headShape <- circleFun(c(0, 0), round(max(electrodeLocs$x)), npoints = 100) # 0
nose <- data.frame(x = c(-0.075,0,.075),y=c(.495,.575,.495))

gridRes = 60 #for interpolation

locs <- ggplot(headShape,aes(x,y))+
  geom_path()+
  geom_text(data = electrodeLocs,
            aes(x, y, label = channel))+
  geom_line(data = nose,
            aes(x, y, z = NULL))+
  theme_topo()+
  coord_equal()

```


# Topoplot of each significant negative cluster for memory quality effect

```{r,warning=FALSE,message=FALSE}

# Cluster 1: 798.83 - 917.97 ms, 15.74 - 30 Hz
cluster1 <- subset(allData, time >= 798.83 & time <= 917.97)
cluster1 <- subset(cluster1, freq >= 15.74 & freq <= 30)

# Summarize cluster 1 t-values
topo.cluster1 <- cluster1 %>%
  group_by(channel) %>%
  summarize(meanbeta = mean(mean.beta),
            pvalue = mean(correctedP.neg, na.rm = T),
            tvalue = mean(tvalue))

# Cluster 2: 1125 - 2277.34 ms, 9.53 - 30 Hz
cluster2 <- subset(allData, time >= 1125 & time <= 2277.34)
cluster2 <- subset(cluster2, freq >= 9.53 & freq <= 30)

# Summarize cluster 2 t-values
topo.cluster2 <- cluster2 %>%
  group_by(channel) %>%
  summarize(meanbeta = mean(mean.beta),
            pvalue = mean(correctedP.neg, na.rm = T),
            tvalue = mean(tvalue))

# Cluster 3: 2839.84 - 3105.47 ms, 5.37 - 16.91 Hz
cluster3 <- subset(allData, time >= 2839.84 & time <= 3105.47)
cluster3 <- subset(cluster3, freq >= 5.37 & freq <= 16.91)

# Summarize cluster 2 t-values
topo.cluster3 <- cluster3 %>%
  group_by(channel) %>%
  summarize(meanbeta = mean(mean.beta),
            pvalue = mean(correctedP.neg, na.rm = T),
            tvalue = mean(tvalue))

```


# Create topoplots for each cluster

```{r,warning=FALSE,message=FALSE}

## Topoplot cluster 1
# add electrode data
singleTimepoint <- topo.cluster1 %>% left_join(electrodeLocs, by = "channel")
gridRes <- 67 # Specify the number of points for each grid dimension i.e. the resolution/smoothness of the interpolation
tmpTopo <- with(singleTimepoint,
                interp(x = x, y = y, z = tvalue, 
                       xo = seq(min(x)*2,
                                max(x)*2,
                                length = gridRes),
                       yo = seq(min(y)*2,
                                max(y)*2,
                                length = gridRes),
                       linear = FALSE,
                       extrap = TRUE)
                ) 
interpTopo <- data.frame(x = tmpTopo$x, tmpTopo$z)
names(interpTopo)[1:length(tmpTopo$y)+1] <- tmpTopo$y
interpTopo <- gather(interpTopo,
                    key = y,
                    value = tvalue, 
                    -x,
                    convert = TRUE)

interpTopo$incircle <- sqrt(interpTopo$x^2 + interpTopo$y^2) < .7 # mark grid elements that are outside of the plotting circle

interpTopo <- interpTopo[interpTopo$incircle,] #remove the elements outside the circle

maskRing <- circleFun(diameter = 1.42) #create a circle round the outside of the plotting area to mask the jagged edges of the interpolation

# subset significant channels to graph with different dot shape in topoplot
sig.channels <- subset(singleTimepoint, pvalue <= 0.025)

## topoplot of MQ negative cluster 1 
akima.cluster1 <- ggplot(interpTopo,
                    aes(x = x, y = y, fill = tvalue) #CHANGE STAT
                    ) +
  geom_raster() +
  stat_contour(aes(z = tvalue), #CHANGE STAT
               colour = "black",
               binwidth = 0.5) +
  theme_topo()+
  scale_fill_gradientn(colours = jet.colors(10),
                       limits = c(-2,2),
                       guide = "colourbar",
                       oob = squish) + 
  geom_path(data = maskRing,
            aes(x, y, z = NULL, fill =NULL),
            colour = "white",
            size = 6) +
  geom_path(data = headShape,
            aes(x, y, z = NULL, fill = NULL),
            size = 1.5)+
  geom_path(data = nose,
            aes(x, y, z = NULL, fill = NULL),
            size = 1.5)+
  geom_point(data = singleTimepoint,
             aes(x, y),
             size = 1.5)+
  geom_point(data = sig.channels,
             aes(x, y),
             size = 1.2,
             color = "white",
             shape = 4,
             stroke = 1.2)+
  coord_equal()+
  ggtitle("Cluster 1")+
  labs(fill = expression(paste(italic("t"), "-value")))+
  theme(text=element_text(size=24, family="Avenir"),
        panel.background = element_rect(fill = "white", colour = "white"), # Set panel background to white
        plot.background = element_rect(fill = "white", colour = "white"), # Set plot background to white
        legend.position = "none",
        plot.title = element_text(vjust = -2),
        plot.caption = element_text(size = 14)) 


akima.cluster1


## Topoplot cluster 2
# add electrode data
singleTimepoint <- topo.cluster2 %>% left_join(electrodeLocs, by = "channel")
gridRes <- 67 # Specify the number of points for each grid dimension i.e. the resolution/smoothness of the interpolation
tmpTopo <- with(singleTimepoint,
                interp(x = x, y = y, z = tvalue, 
                       xo = seq(min(x)*2,
                                max(x)*2,
                                length = gridRes),
                       yo = seq(min(y)*2,
                                max(y)*2,
                                length = gridRes),
                       linear = FALSE,
                       extrap = TRUE)
                ) 
interpTopo <- data.frame(x = tmpTopo$x, tmpTopo$z)
names(interpTopo)[1:length(tmpTopo$y)+1] <- tmpTopo$y
interpTopo <- gather(interpTopo,
                    key = y,
                    value = tvalue, 
                    -x,
                    convert = TRUE)

interpTopo$incircle <- sqrt(interpTopo$x^2 + interpTopo$y^2) < .7 # mark grid elements that are outside of the plotting circle

interpTopo <- interpTopo[interpTopo$incircle,] #remove the elements outside the circle

maskRing <- circleFun(diameter = 1.42) #create a circle round the outside of the plotting area to mask the jagged edges of the interpolation

# subset significant channels to graph with different dot shape in topoplot
sig.channels <- subset(singleTimepoint, pvalue <= 0.025)

## topoplot of MQ negative cluster 1 
akima.cluster2 <- ggplot(interpTopo,
                    aes(x = x, y = y, fill = tvalue) #CHANGE STAT
                    ) +
  geom_raster() +
  stat_contour(aes(z = tvalue), #CHANGE STAT
               colour = "black",
               binwidth = 0.5) +
  theme_topo()+
  scale_fill_gradientn(colours = jet.colors(10),
                       limits = c(-2,2),
                       guide = "colourbar",
                       oob = squish) + 
  geom_path(data = maskRing,
            aes(x, y, z = NULL, fill =NULL),
            colour = "white",
            size = 6) +
  geom_path(data = headShape,
            aes(x, y, z = NULL, fill = NULL),
            size = 1.5)+
  geom_path(data = nose,
            aes(x, y, z = NULL, fill = NULL),
            size = 1.5)+
  geom_point(data = singleTimepoint,
             aes(x, y),
             size = 1.5)+
  geom_point(data = sig.channels,
             aes(x, y),
             size = 1.2,
             color = "white",
             shape = 4,
             stroke = 1.2)+
  coord_equal()+
  ggtitle("Cluster 2")+
  labs(fill = expression(paste(italic("t"), "-value")))+
  theme(text=element_text(size=24, family="Avenir"),
        panel.background = element_rect(fill = "white", colour = "white"), # Set panel background to white
        plot.background = element_rect(fill = "white", colour = "white"), # Set plot background to white
        legend.position = "none",
        plot.title = element_text(vjust = -2),
        plot.caption = element_text(size = 14)) 


akima.cluster2


## Topoplot cluster 3
# add electrode data
singleTimepoint <- topo.cluster3 %>% left_join(electrodeLocs, by = "channel")
gridRes <- 67 # Specify the number of points for each grid dimension i.e. the resolution/smoothness of the interpolation
tmpTopo <- with(singleTimepoint,
                interp(x = x, y = y, z = tvalue, 
                       xo = seq(min(x)*2,
                                max(x)*2,
                                length = gridRes),
                       yo = seq(min(y)*2,
                                max(y)*2,
                                length = gridRes),
                       linear = FALSE,
                       extrap = TRUE)
                ) 
interpTopo <- data.frame(x = tmpTopo$x, tmpTopo$z)
names(interpTopo)[1:length(tmpTopo$y)+1] <- tmpTopo$y
interpTopo <- gather(interpTopo,
                    key = y,
                    value = tvalue, 
                    -x,
                    convert = TRUE)

interpTopo$incircle <- sqrt(interpTopo$x^2 + interpTopo$y^2) < .7 # mark grid elements that are outside of the plotting circle

interpTopo <- interpTopo[interpTopo$incircle,] #remove the elements outside the circle

maskRing <- circleFun(diameter = 1.42) #create a circle round the outside of the plotting area to mask the jagged edges of the interpolation

# subset significant channels to graph with different dot shape in topoplot
sig.channels <- subset(singleTimepoint, pvalue <= 0.025)

## topoplot of MQ negative cluster 1 
akima.cluster3 <- ggplot(interpTopo,
                    aes(x = x, y = y, fill = tvalue) #CHANGE STAT
                    ) +
  geom_raster() +
  stat_contour(aes(z = tvalue), #CHANGE STAT
               colour = "black",
               binwidth = 0.5) +
  theme_topo()+
  scale_fill_gradientn(colours = jet.colors(10),
                       limits = c(-2,2),
                       guide = "colourbar",
                       oob = squish) + 
  geom_path(data = maskRing,
            aes(x, y, z = NULL, fill =NULL),
            colour = "white",
            size = 6) +
  geom_path(data = headShape,
            aes(x, y, z = NULL, fill = NULL),
            size = 1.5)+
  geom_path(data = nose,
            aes(x, y, z = NULL, fill = NULL),
            size = 1.5)+
  geom_point(data = singleTimepoint,
             aes(x, y),
             size = 1.5)+
  geom_point(data = sig.channels,
             aes(x, y),
             size = 1.2,
             color = "white",
             shape = 4,
             stroke = 1.2)+
  coord_equal()+
  ggtitle("Cluster 3")+
  labs(fill = expression(paste(italic("t"), "-value")))+
  theme(text=element_text(size=24, family="Avenir"),
        panel.background = element_rect(fill = "white", colour = "white"), # Set panel background to white
        plot.background = element_rect(fill = "white", colour = "white"), # Set plot background to white
        legend.title.position = "top",
        legend.title = element_text(hjust = 0.5),
        legend.margin = margin(0,0,0,0),
        legend.box.margin=margin(-25,0,0,0),
        legend.position = "bottom",
        plot.title = element_text(vjust = -2),
        plot.caption = element_text(size = 14)) 


akima.cluster3


```


### Save MQ TF figures

```{r warning = FALSE, message = FALSE}

TFfigures <- ggarrange(MQ_freqbandslog, alpha.MQ, beta.MQ, nrow = 3, heights = c(2,1,1), labels = c("A", "", ""), font.label = list(color = "black", size = 26, family = "Arial", face = "bold"))
TFfigures

topo_MQTF_figure <- ggarrange(akima.cluster1, akima.cluster2, akima.cluster3, nrow = 3, ncol = 1, heights = c(1,1,1.3), labels = c("B", "", ""), font.label = list(color = "black", size = 26, family = "Arial", face = "bold"))
topo_MQTF_figure

all.figures <- ggarrange(TFfigures, topo_MQTF_figure, ncol = 2, widths = c(2,0.9))
all.figures

# save figure to output directory
ggsave("Figure5.tiff", path = figureDir, width = 11, height = 8)
ggsave("Figure5.png", path = figureDir, width = 11, height = 8)

```